---
output: html_document
---

# STAT4001 Homework 2

```{r, echo=FALSE}
library(glmnet)
```

```{r}
set.seed(1)
X = rnorm(100,0,1)
epsilon = rnorm(100,0,0.1)
Y = 1+X+X^2+X^3+epsilon
grid = 10^seq(10,-2,length=100)
```

Now generate matrix:

```{r}
Xmat = X
for (i in 2:10) {
	Xmat = cbind(Xmat,X^i)
}

```{r}
lasso.mod = glmnet(Xmat,Y,alpha=1,lambda=grid)
plot(lasso.mod)
```

```{r, echo=FALSE}
train = sample(1:nrow(Xmat),nrow(Xmat)/2)
test = (-train)
Y.test = Y[test]
Y.train = Y[train]
```

```{r}
cv.out = cv.glmnet(Xmat[train,],Y.train,alpha=1)
plot(cv.out)
```

```{r}
bestlam = cv.out$lambda.min
bestlam
```

```{r}
lasso.pred = predict(lasso.mod,s=bestlam,newx=Xmat[test,])
mean((lasso.pred-Y.test)^2)
out = glmnet(Xmat,Y,alpha=1,lambda=grid)
lasso.coef = predict(out,type="coefficients",s=bestlam)[1:11,]
lasso.coef
```

Part d:

```{r}
Ynew = 1+X^7+epsilon
lasso.mod = glmnet(Xmat,Ynew,alpha=1,lambda=grid)
plot(lasso.mod)

```{r, echo=FALSE}
train = sample(1:nrow(Xmat),nrow(Xmat)/2)
test = (-train)
Ynew.test = Ynew[test]
Ynew.train = Ynew[train]
```

```{r}
cv.out = cv.glmnet(Xmat[train,],Ynew.train,alpha=1)
plot(cv.out)
```

```{r}
bestlam = cv.out$lambda.min
bestlam
```

```{r}
lasso.pred = predict(lasso.mod,s=bestlam,newx=Xmat[test,])
mean((lasso.pred-Ynew.test)^2)
out = glmnet(Xmat,Ynew,alpha=1,lambda=grid)
lasso.coef = predict(out,type="coefficients",s=bestlam)[1:11]
lasso.coef
```
